---
title: "Assignment 1"
output:
  word_document: default
  html_notebook: default
---

```{r}
# https://www.stats.govt.nz/large-datasets/csv-files-for-download/ #
# Import the dataset into R #
dataset <- read.csv("C:\\Users\\imcguire\\Downloads\\annual-enterprise-survey-2021-financial-year-provisional-csv.csv")
head(dataset)

```
```{r}
# Print out descriptive statistics for a selection of quantitative and categorical variables. #
# Quantitative variables #
quant_vars <- c("Year", "Value")
cat_vars <- c("Variable_code", "Variable_name")

# Summary statistics for quantitative variables #
summary_quant <- summary(dataset[, quant_vars])
print(summary_quant)

# Frequency table for categorical variables #
for (var in cat_vars) {
  cat_freq <- table(dataset[, var])
  print(paste("Frequency table for", var))
  print(cat_freq)
}
```
```{r}
# Transform a variable #
dataset$LogYear <- log(dataset$Year)
```

```{r}
# Histogram for Value #
dataset$Value <- as.integer(dataset$Value)
hist(dataset$Value, main="Value Distribution", xlab="Value")

# Scatterplot for Value vs. Year #
plot(dataset$Value, dataset$Year, main="Scatterplot: Value vs. Year", xlab="Value", ylab="Year")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
